Late Fusion via Subspace Search with Consistency Preservation

### 2018-07-07 BACKUP/cvpr-2017/Fusion-cvpr2017-RebuttalKit/rebuttal-fusion.txt

\section{Overall}
We thank all the reviewers.
R3 is positive.
R1 has some suggestions about technical analysis.
R2 ...
We take the comments seriously and will carefully revise the paper. 
Typos will be corrected. Code will be released.

\section{For Assigned Reviewer 1}

Q1: The technical part in Sec 3.2 a little over-sold.

A1:
First, ALM is usually used for convex problem~[50] and (G. Liu etal, TPAMI 2013),
but our Problem~(2) is non-convex.
Therefore, the convergence behavior of Algorithm 1 may be unclear.
Second, to make the paper self-contained, it is necessary to present every phase of Algorithm~1.
Third, we explicitly indicate the connection between the definition (Eq (8)) and the computation (Algorithm 2) of Riemannian gradient by presenting Lemma 1.
This did not present in the previous work.
To make the contributions more clear, we will provide more references and explain the difference between our paper and previous works as suggested.

\section{For Assigned Reviewer 2}

Q1. Weakness of technical novelty and significance}

A1:
Previous works~[50] that formulate late fusion as matrix completion are based on nuclear norm.
They cannot handle large-scale problems.
We thus propose an efficient matrix factorization-based algorithm.
On one hand, previous matrix factorization algorithms only consider smooth loss rather than non-smooth robust loss.
On the other hand, previous ALM-related papers consider convex problems, so it is unclear how its convergence behavior is in the non-convex case.
To address both issues, this paper proposes a new matrix factorization-based algorithm to handle non-smooth loss and provides convergence analysis.

Q2. Problem~(6) can be solved by SVD or alternating minimization.

A2:
In P. Jain et al., 2013, the authors provide global optimality of $\epsilon$-solution (i.e. the loss function satisfies $|| M - X ||_F^2 \leq \epsilon$. See Theorem 2.5 in this paper.) of alternating minimization, rather than a strictly unique global optimum.
Our paper provides the convergence guarantee of a strictly local minimum where the gradient w.r.t. $\bX$ vanishes.
Thus, their result and ours may not be comparable.

Q3. Algorithms 2 and 3 may be unnecessary.}

A3: 
The algorithm should be self-contained and it may be necessary to describe solutions for any formula.
But we are pleasure to simplify our presentation.

Q4. Will the sequence of $\lambda_k$ be bounded as required, or that accumulation points even exist?

A4:
Boundedness of $\blambda_k$:
After the inner loop (Step 1,2) of Algorithm 1 converges, we have 
$\calL(\bX_{k+1}, \bE_{k+1}, \blambda_{k}, \mu_{k}) = ||\bE_{k+1}||_{1,2} + \frac{1}{2\mu_{k}}(||\blambda_{k+1}||_{F}^2 - ||\blambda_{k}||_{F}^2)$.
Due to the convergence and $\frac{1}{\mu_{k}} \rightarrow 0$ when $k \rightarrow + \infty$, we have $||\blambda_{k+1}||_{F}^2 - ||\blambda_{k}||_{F}^2 < +\infty$, and thus the boundedness of $\blambda_{k}$.

As proof of Theorem 1, $k \rightarrow \infty$, $\bL - \bX_{k} - \bE_{k}$ and the gradient of $\calL$ w.r.t. $\bX_{k}$ vanishes.
Thus $\bX_{k}$ is a stationary point as long as $\bX_{k}$ is generated according to Algorithm 1.

Q5. Empirical issues in Table 1 and Table 5.

A5:
As shown in Table 1, our method outperforms LPBoost significantly on UCF-101 and CIFAR-100,
and our fusion method performs well on most datasets comparing with other methods.

Q6. Why not compare against other SOTA fusion methods in Table.5, but just single model results ?

A6:
We compare our method with state-of-the-art single models in Sec 4.5 and list the test error in Table 5 to verify the improvement of our late fusion algorithm.
Test error of competing models are referred from the original papers.
Comparison between our method and other late fusion methods is performed specifically in Sec 4.3 (Table 1 and Table 2).

Q7. Reproducibility - It is obvious that a fused model is better than the best single model.

A7:
It can't guarantee that a fused model can definitely perform better than the best single model.
By comparing with single models, we aim to verify the effectiveness of our method.
The best single model performance on CIFAR-10 is currently in~\cite{xie2016aggregated} (test error 3.58).
Our method fuse multiple single models which all perform worse than~~\cite{xie2016aggregated}, but can achieve low test error on CIFAR-10 (3.47 in Table 5).
This demonstrates the benefit of a good late fusion method.

\section{For Assigned Reviewer 3}

Q1. Discuss how the $\ell_{1,2}$ norm helps with outliers; show what happens if you use $l_2$ norm as usual}

A1:
As indicated in lines 106-110, $\ell_{1,2}$ loss preserves the fidelity within columns of $\bL$ and filters out those columns with low fidelity.
$\ell_{2}$ loss is known to be sensitive to outliers.
$\ell_{2}$ loss is not robust to large outliers and the result may be biased to them.
We will add a $\ell_{2}$ variant of our approach as a baseline in the revised version to illustrate the difference.

Q2. Discussions about classifiers are adversarial.

A2:
In fact, Sec 4.1 and Figure 2 show a similar situation: 40\% predicted labels are switched from ground-truth (adversarial classifiers).
In this situation, our algorithm performs well and recovers most of the results.

Q3. Add classifiers that predict uninterested things.}

A3:
Thanks for this interesting and helpful suggestion.
We will investigate this problem in our future work.

### 2018-07-07 BACKUP/cvpr-2017/RLF_MF_v2.tex
update for minor

\def\year{2017}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{color}
\usepackage{epstopdf}
\usepackage{bm}
%\usepackage[vlined,boxed,ruled]{algorithm2e}
\usepackage{url}
\usepackage{xspace}

@@

\usepackage{aaai17}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}

@@

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}
 \begin{document}

% The file aaai.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

%\title{Consistent Late Fusion for Visual Recognition}
\title{Late Fusion via Subspace Search with Consistency Preservation}
%% Efficient

\author{AAAI Press\\
Association for the Advancement of Artificial Intelligence\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\
}

\maketitle

\begin{abstract}
% First: A big picture of the scenario which we would consider
In many real-world applications, data can be represented in multiple ways or multi-view features,
in order to describe various characteristics of data.
In this way, it could often improve the prediction performance by taking advantage of these feature together.
% Second: what BIG problem would we like to solve?
Late fusion, which combines the predictions of multiple features, is a commonly used approach to make the final decision for a test instance.
% Third: specify the detailed problem: find a precise position for our paper
However, it is ubiquitous that different features would dispute on the data, which results in performance degeneration.
So there is a requirement of outlier rejection for late fusion algorithms.
% Fourth: general introduction of our method
In this paper, we propose an efficient matrix factorization based approach to fuse predictions from multiple sources,
which could avoid the performance degeneration caused by the controversy of multiple features on test data.
% Some unvalued sentence(s)
Extensive experiments demonstrate that the proposed method is effective to remove outliers and improve fusion performance.

@@

%% late fusion is a common sigle model -> single feature, 介绍late fusion
Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features.
A commonly used method is to learn weights for predictions from various features to combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
To deal with this issue, therefore, some works formulate it as a robust low rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.

To prevent from the expensive nuclear norm minimization, in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low rank label matrix.
As for outlier detection, as shown in Figure~\ref{fig:framework} (notations are introduced shortly), we apply robust $\ell_{1,2}$ loss to remove the outlier columns in the label matrix.
Most existing matrix factorization optimization methods, however, only consider smooth loss functions, rather than the nonsmooth loss.
We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to nonsmooth problems.
The main contributions are summarized as below:
\begin{itemize}
  %\item We propose an efficient late fusion algorithm based on matrix factorization.
  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem based on matrix factorization, which intuitively preserves the consistency of predictions from different sources.
  \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss.
  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
\end{itemize}

@@

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
In~\cite{vandereycken2013lowrank}, the authors propose a low rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low rank matrix completion by exploiting the low rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm is proposed to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.

%% Latent Fusion,

@@

\begin{figure}[ht]
\centering\includegraphics[width=0.45\textwidth]{resource/frame_work.pdf}
\caption{Framework (example of $n=10, \calC=3, m=3$)}
\label{fig:framework}
\end{figure}

@@

Suppose there are $n$ testing instances and $\calC$ classes.
We denote each instance as $x_i \in \dsR^{d}$ where $1 \leq i \leq n$.
Assume that we have already trained $m$ classifiers, \ie. $f_1, f_2, ... f_m$.
Then by applying each single classifier $f_j$ on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times m}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
Let $\bL = [ \bL_1, \bL_2, ..., \bL_\calC ]$.
%%On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank constraint on $\bL$.
On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
{\small
$$ || \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 } . $$
}
\noindent
Thus, the proposed model can be written as below:
{\small
\begin{align}\label{eq:l12_rankconstraint}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
  \st ~&~ \rank(\bX) = p   ,
\end{align}
}
\noindent
where $\bX \in \dsR^{n \times m\calC}$ is the underlying low rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
and $p$ is a scalar.
In our setting, to preserve the consistency among various classifiers, we set $p = \calC$.

It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
We hence transform the original problem as a matrix factorization formulation as below:
{\small
\begin{align}\label{eq:l12_mf}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}   \nonumber \\
         \st ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}  .
\end{align}
}
\noindent
Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a nonsmooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).

%\begin{small}
\begin{algorithm}[ht]

@@

By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:l12_mf}) as below:
{\small
\begin{align}\label{eq:mf_l21_constrained}
  \min_{\bE, \bX} ~&~ || \bE ||_{1,2}      \nonumber \\
  \st             ~&~ \bE = \bL - \bX  ,   \nonumber \\
                  ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m \calC}
\end{align}
}
\noindent
The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
{\small
\begin{align}\label{eq:lagrangian_l21}
  \calL (\bX, \bE, \blambda, \mu) = &~ || \bE ||_{1,2} + \langle \blambda, \bL - \bX - \bE \rangle      \nonumber \\
                                    & + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2
\end{align}
}
\noindent
where $\bX = \bU \bV$, $\mu$ is a scalar,
and $\blambda \in \dsR^{n \times m\calC}$ are the Lagrangian multipliers.
Here $\langle \bA, \bB \rangle$ is the inner product of $\bA \in \dsR^{m \times n}$ and $\bB \in \dsR^{m \times n}$, and defined as $\langle \bA, \bB \rangle = \sum_{i=1}^{n} \sum_{j=1}^{m} \bA_{ij} \bB_{ij}$.
Then we can update $\bX$ and $\bE$ alternatively, which is summarized in Algorithm~\ref{alg:alm_mf}.

\begin{theorem}
\label{theorem:alm_convergence}
  Suppose that the sequence $\{ \blambda_{k} \}$ is bounded, any accumulation point $(\bX^*, \bE^*)$ of Algorithm~\ref{alg:alm_mf} is a stationary point.
\end{theorem}

@@

Particularly, to update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
{\small
\begin{align}\label{eq:langrangian_wrt_X}
  \calL (\bX) = & \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
              %= & \frac{\mu}{2} \Big( || \bL - \bX - \bE ||_F^2 + \frac{2}{\mu} \langle \blambda, \bL - \bX - \bE \rangle + \frac{|| \blambda ||_F^2}{\mu^2} \Big)    \nonumber   \\
              %  & - \frac{\mu}{2} \frac{|| \blambda ||_F^2}{\mu^2}   \nonumber \\
              %= & || \bL - \bX - \bE + \frac{\blambda}{\mu} ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   \nonumber \\
              = & || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bM = \bL - \bE + \frac{\blambda}{\mu}$.
Hence, we derive the following subproblem \wrt. $\bX$:
{\small
\begin{align}\label{eq:subproblem_wrt_X}
  \min_{\bX} ~&~ || \bM - \bX ||_F^2    \nonumber \\
  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}   .
\end{align}
}
\noindent
%Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt. $\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}.
Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function of $\bX$.
We thus propose to solve the subproblem by exploiting Riemannian geometry of smooth fixed-rank matrices, which is briefly presented below.

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{amsthm,mathrsfs,amsfonts,dsfont}
\usepackage{algorithm}
\usepackage{algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{epstopdf}
\usepackage{bm}
%\usepackage[vlined,boxed,ruled]{algorithm2e}
\usepackage{url}
\usepackage{xspace}

@@

@@

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{3651} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE3
\title{Late Fusion via Subspace Search with Consistency Preservation}
\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

\begin{abstract}
In many real-world applications, data can be represented in multiple ways or multi-view features,
in order to describe various characteristics of data.
In this way, it could often improve the prediction performance by taking advantage of these feature together.
Late fusion, which combines the predictions of multiple features, is a commonly used approach to make the final decision for a test instance.
However, it is ubiquitous that different features would dispute on the data, which results in performance degeneration.
Therefore, there is a requirement of outlier rejection while preserving consistency among different classifier results.
In this paper, we propose an efficient matrix factorization based approach to fuse predictions from multiple sources,
which could avoid the performance degeneration caused by the controversy of multiple features on test data.
Extensive experiments demonstrate that the proposed method is effective to remove outliers and improve fusion performance.

@@

%% late fusion is a common sigle model -> single feature, 介绍late fusion
Late fusion, a typical approach to obtaining the final decision on testing data, aims to fuse the predictions from different features.
A commonly used method is to learn weights for predictions from various features to combine them, which has a number of variations~\cite{gehler2009feature,xuiccv2013feature,lai2015learning}.
Among these algorithms, multiple kernel learning (MKL)~\cite{lanckriet2004learning,Rakotomamonjy2008Simplemkl} is often used to train such a weighted combination.
However, a single feature may produce corrupted predictions on some data, which likely degenerates performance.
To deal with this issue, therefore, some works formulate it as a robust low-rank matrix recovery problem~\cite{gaoijcai2016robust,ye2012robust} by nuclear norm minimization.
Nevertheless, nuclear norm minimization applied in these works requires singular value decompositions (SVDs), which would be computationally unaffordable for large matrices.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.48\textwidth]{resource/frame_work.pdf}
\end{center}
\caption{Framework of our late fusion algorithm.
In this example, there are 10 instances 3 classifiers and 3 classes.
Predictions of each classifier are converted to a binary indicator matrix,
denoted by $L_1$, $L_2$ and $L_3$.
Let $L = [L_1, L_2, L_3]$ be the label matrix.
Our algorithm detects and removes the outliers on $L$ and then recover the underlying low-rank subspace of $L$ as the prediction for testing instances.
We finally apply a post-processing method to generate the fused results.
%First, there are $\calC=3$ classifiers' results for $n=10$ instances.
%Each of them are converted into ``binary'' indicators from the soft prediction results, as $L = [L_1, L_2, L_3]$.
%Then, our ALM-based optimization process the binary indicator matrix into a recovered matrix $X$,
%which can be treated as soft prediction scores for testing instances.
%Finally, the fused prediction results are generated by a post-processing method.
}
\label{fig:framework}
\end{figure}

To prevent from the expensive nuclear norm minimization,
in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
%As for outlier detection, our framework is shown in Figure~\ref{fig:framework} (notations are introduced shortly).
Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
As for outlier detection,
we propose to filter out these inconsistent predictions on specific classes of models (See Fig.~\ref{fig:framework}.
Notations are introduced shortly.).
%as shown in Figure~\ref{fig:framework} (notations are introduced shortly),
Due to the fact that the $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction,
we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
Furthermore, most existing matrix factorization optimization methods,
however, only consider smooth loss functions, rather than the nonsmooth loss.
We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to nonsmooth problems.
The main contributions are summarized as below:
\begin{itemize}
  %\item We propose an efficient late fusion algorithm based on matrix factorization.
  \item We formulate the late fusion problem as a fixed-rank robust matrix recovery problem based on matrix factorization, which intuitively preserves the consistency of predictions from different sources.
  \item We propose an ALM based algorithm to extend existing matrix factorization algorithms from smooth least square loss to nonsmooth $\ell_{1,2}$ loss. 
  %\item Our proposed algorithm is more efficient than most state-of-the-art late fusion methods.
  %It is capable of handling large scale problems.
  \item Empirical studies show significantly improvement of our proposed method compared to existing late fusion algorithms.
\end{itemize}

@@

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
In~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.

Some other fusion algorithms are propsed for specific tasks, which would be hard to extend to general problems.
In~\cite{zheng2015query}, the authors estimate a feature’s effectiveness in a query-adaptive manner for image retrieval problems,
and they combine the scores of multiple features weighted by their effectiveness.
In~\cite{zha2015exploiting}, they use fusion features scores of different CNN layers and encoded features impove the accuracy of action recognition.
In~\cite{feichtenhofer2016convolutional}, the authors explore a variety of fusion methods to combine spatial and temporal CNN models, significantly improving the performance of two-stream network~\cite{simonyan2014two}.
\cite{wangmodality} proposes a framework use high-dimensional Fisher Vector features from RGB, HHA and surface normal modalities to effectively achieve state-of-the-art scene classification performance.
\cite{Wang_Transformation,tapaswi2015movieqa,yaohighlight} use some simple strategies to choose specific weight for different scores from multiple features.

%% Feature 
%Some algorithms exploit the early fusion methods, \textit{i.e.} feature fusion,
%to improve the performance of their CNN architectures.

@@

@@

Suppose there are $n$ testing instances and $\calC$ classes.
We denote each instance as $x_i \in \dsR^{d}$ where $1 \leq i \leq n$.
Assume that we have already trained $m$ classifiers, \ie. $f_1, f_2, ... f_m$.
Then by applying each single classifier $f_j$ on the entire testing data, one can derive an indicator matrix $\bL_j \in \dsR^{n \times \calC}$, where $\bL_{j, ic} = 1$ if the $i$-th instance is assigned to the $c$ class, otherwise $\bL_{j, ic} = 0$ (as shown in Figure~\ref{fig:framework}).
Let $\bL = [ \bL_1, \bL_2, ..., \bL_m ]$.
%%On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank-$m$ constraint on $\bL$.
On one hand, we aim to preserve the consistency among $m$ classifiers, so we introduce a rank constraint on $\bL$.
On the other hand, to catch the outlier columns, we apply robust $\ell_{1, 2}$ loss, which is computed by
{
\begin{align}
|| \bX ||_{1,2} = \sum_{j = 1}^{m\calC} \sqrt{ \sum_{i = 1}^{n} \bX_{ij}^2 }
\end{align}
}
\noindent
Thus, the proposed model can be written as below:
{
\begin{align}\label{eq:l12_rankconstraint}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
  \st ~&~ \rank(\bX) = p
\end{align}
}
\noindent
where $\bX \in \dsR^{n \times m\calC}$ is the underlying low-rank label matrix to be recovered, $\rank(\bX)$ obtains the rank of $\bX$,
and $p$ is a scalar.
In our setting, to preserve the consistency among various classifiers, we set $p = \calC$.

It is difficult to optimize Problem~(\ref{eq:l12_rankconstraint}) directly due to the presence of the rank constraint.
We hence transform the original problem as a matrix factorization formulation as below:
{
\begin{align}\label{eq:l12_mf}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}   \nonumber \\
         \st ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}  .
\end{align}
}
\noindent
Nevertheless, existing matrix factorization algorithms focus on smooth loss functions, rather than a nonsmooth $\ell_{1,2}$ loss function~\cite{tanicml2014riemannian,vandereycken2013lowrank,Wen2012,ngonips2012scaled,rtrmc2011boumal}.
In the following section, we present an ALM optimization framework to solve Problem~(\ref{eq:l12_mf}).

\begin{algorithm}[ht]

@@

By introducing a new variable $\bE = \bL - \bX$, we can develop Problem~(\ref{eq:l12_mf}) as below:
{
\begin{align}\label{eq:mf_l21_constrained}
  \min_{\bE, \bX} ~&~ || \bE ||_{1,2}      \nonumber \\
  \st             ~&~ \bE = \bL - \bX  ,   \nonumber \\
                  ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m \calC}
\end{align}
}
\noindent
The augmented Lagrangian function of Problem~(\ref{eq:l12_mf}) is constructed as below
{
\begin{align}\label{eq:lagrangian_l21}
  \calL (\bX, \bE, \blambda, \mu) = &~ || \bE ||_{1,2} + \langle \blambda, \bL - \bX - \bE \rangle      \nonumber \\
                                    & + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2
\end{align}
}
\noindent
where $\bX = \bU \bV$, $\mu$ is a scalar,
and $\blambda \in \dsR^{n \times m\calC}$ are the Lagrangian multipliers.
Here $\langle \bA, \bB \rangle$ is the inner product of $\bA \in \dsR^{m \times n}$ and $\bB \in \dsR^{m \times n}$, and defined as $\langle \bA, \bB \rangle = \sum_{i=1}^{n} \sum_{j=1}^{m} \bA_{ij} \bB_{ij}$.
Then we can update $\bX$ and $\bE$ alternatively, which is summarized in Algorithm~\ref{alg:alm_mf}.

\begin{theorem}
\label{theorem:alm_convergence}
  %Suppose that the sequence $\{ \blambda_{k} \}$ is bounded, any accumulation point
  %\footnote{the limit point of a sequence}~\cite{oh2016partial} $(\bX^*, \bE^*)$ of Algorithm~\ref{alg:alm_mf} is a stationary point.
  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
  and $\{\blambda_k\}$ is bounded. Any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
\end{theorem}

@@

Particularly, to update $\bX$, we have the following augmented Lagrangian function \wrt. $\bX$:
{
\begin{align}\label{eq:langrangian_wrt_X}
  \calL (\bX) = & \langle \blambda, \bL - \bX - \bE \rangle + \frac{\mu}{2} || \bL - \bX - \bE ||_F^2  \nonumber  \\
              = & \frac{\mu}{2} || \bM - \bX ||_F^2 - \frac{1}{2\mu}|| \blambda ||_F^2   ,
\end{align}
}
\noindent
where $\bM = \bL - \bE + \frac{\blambda}{\mu}$.
Hence, we derive the following subproblem \wrt. $\bX$:
{
\begin{align}\label{eq:subproblem_wrt_X}
  \min_{\bX} ~&~ || \bM - \bX ||_F^2    \nonumber \\
  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{n \times p},~\bV \in \dsR^{p \times m\calC}   .
\end{align}
}
\noindent
%Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function \wrt. $\bX$, thus can be efficiently solved by existing fixed-rank matrix factorization optimization algorithms, such as LRGeomCG~\cite{vandereycken2013lowrank}.
Problem~(\ref{eq:subproblem_wrt_X}) contains a smooth loss function of $\bX$.
We thus propose to solve the subproblem by exploiting Riemannian geometry of smooth fixed-rank matrices, which is briefly presented below.

The key idea of manifold optimization is that update of $\bX$ is always performed on the same manifold, which ensures the rank of $\bX$ unchanged as the optimization iterates.
In other words, we search the solution for $\bX$ in a low-rank subspace.
Let $r$ be a known scalar.
A smooth manifold of fixed-rank-$r$ matrices is defined as~\cite{vandereycken2013lowrank}:
{
\begin{eqnarray}
\M_{r} &=& \{\bX\in \R^{n\times m\calC}: \rank(\bX) = r\} \nonumber \\
       &=& \{\U\diag(\bsigma)\V^{\trsp}: \U \in \textrm{St}_{r}^{n}, \V \in
           \textrm{St}_{r}^{m\calC}, ||\bsigma||_0 = r\} \nonumber
\end{eqnarray}
}
\noindent
where $\textrm{St}_{r}^{n} = \{\U \in \R^{n\times r}:
\U^{\trsp}\U = \I \}$ dentoes the Stiefel manifold of $n\times r$ real and orthonormal matrices.
We denote the tangent space by $T_{\bX}\M_{r}$ of $\M_{r}$ at $\bX = \U\diag(\bsigma)\V^{\trsp} \in \R^{n \times m\calC}$,
which is obtained as below
{
\begin{eqnarray}\label{eq:tangent_vector}
&&T_{\bX}\M_{r} =  \{\U\bM\V^{\trsp} \!\!+\! \U_p\V^{\trsp} \!\!+\!
\U\V_p^{\trsp}: \bM \in \R^{r\times r}, \nonumber\\ && \U_p \in \R^{n\times r},
\U_p^{\trsp}\U = \0, \V_p \in \R^{m\calC \times r}, \V_p^{\trsp}\V = \0\}.
\end{eqnarray}
}
\noindent
One can define a metric $g_{\bX}({\bA},{\bB}) = \langle{\bA},{\bB}\rangle$ on $\M_{r}$,
with $\bX \in \M_{r}$ and ${\bA},{\bB} \in T_{\bX}\M_{r}$,
then $\M_{r}$ becomes a Riemannian manifold by restricting
$\langle\bA,\bB\rangle$
to the \emph{tangent bundle}, defined as the disjoint union of all tangent spaces:
$T\M_{r} = \bigcup_{\bX\in \M_{r}}\{\bX\} \times T_{\bX}\M_{r}
         = \! \{(\bX,\bP)\in \R^{n \times m\calC} \times \R^{n \times m\calC}: \bX \in \M_{r}, \bP \in T_{\bX}\M_{r}\}.$
